Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-07-07 paper.tex
Somewhat drastic space reduction
Jack's affiliation.

\author{
    \IEEEauthorblockN{
        Alessio Angius\IEEEauthorrefmark{1}\IEEEauthorrefmark{2},
        Danila Oleynik\IEEEauthorrefmark{1}\IEEEauthorrefmark{5},
        Sergey Panitkin\IEEEauthorrefmark{1}\IEEEauthorrefmark{4},
        Matteo Turilli\IEEEauthorrefmark{1}\IEEEauthorrefmark{2},\\
        Kaushik De\IEEEauthorrefmark{5},
        Alexei Klimentov\IEEEauthorrefmark{4},
        Sarp H. Oral\IEEEauthorrefmark{6},
        Jack C. Wells\IEEEauthorrefmark{6} and
        Shantenu Jha\IEEEauthorrefmark{2}
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{1}First authors, alphabetical order
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{2}Department of Electric and Computer Engineering, Rutgers University, NJ, USA
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{4}Physics Department, Brookhaven National Laboratory, NY, USA
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{5}Physics Department, University of Texas Arlington, TX, USA
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{6}Oak Ridge Leadership Computing Facility, Oak Ridge National Laboratory, TN, USA
    }
}

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
% \author{
%     \IEEEauthorblockN{
%         Author 1\IEEEauthorrefmark{1},
%         Author 2\IEEEauthorrefmark{2},
%         Author 3\IEEEauthorrefmark{3}, 
%         Author 4\IEEEauthorrefmark{3}, 
%         Author 5\IEEEauthorrefmark{4} and
%         Author 6\IEEEauthorrefmark{4}
%     }
%     \IEEEauthorblockA{
%         \IEEEauthorrefmark{1}Department\\Institution, address, email
%     }
%     \IEEEauthorblockA{
%         \IEEEauthorrefmark{2}Department\\Institution, address, email
%     }
%     \IEEEauthorblockA{
%         \IEEEauthorrefmark{3}Department\\Institution, address, email
%     }
%     \IEEEauthorblockA{
%         \IEEEauthorrefmark{4}Department\\Institution, address, email
%     }
% }

@@

% ---------------------------------------------------------------------------
% REFERENCES
% ---------------------------------------------------------------------------
\newpage
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,bibliography}

>>>>

\author{
    \IEEEauthorblockN{
        Alessio Angius\IEEEauthorrefmark{1}\IEEEauthorrefmark{2},
        Danila Oleynik\IEEEauthorrefmark{1}\IEEEauthorrefmark{5},
        Sergey Panitkin\IEEEauthorrefmark{1}\IEEEauthorrefmark{4},
        Matteo Turilli\IEEEauthorrefmark{1}\IEEEauthorrefmark{2},\\
        Kaushik De\IEEEauthorrefmark{5},
        Alexei Klimentov\IEEEauthorrefmark{4},
        Sarp H. Oral\IEEEauthorrefmark{6},
        Jack C. Wells\IEEEauthorrefmark{7} and
        Shantenu Jha\IEEEauthorrefmark{2}
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{1}First authors, alphabetical order
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{2}Department of Electric and Computer Engineering, Rutgers University, NJ, USA
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{4}Physics Department, Brookhaven National Laboratory, NY, USA
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{5}Physics Department, University of Texas Arlington, TX, USA
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{6}Oak Ridge Leadership Computing Facility, Oak Ridge National Laboratory, TN, USA
        }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{7}National Center for Computational Sciences, Oak Ridge National Laboratory, TN, USA
        }
}

@@

% ---------------------------------------------------------------------------
% REFERENCES
% ---------------------------------------------------------------------------
% \newpage
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,bibliography}
